Evolution of ORM Systems: Formal Foundations

### 2013-01-16 doc/description.tex
refactored db and app constructors

The software has to be in consistent state so its users could have benefit from its usage. The state of the software is defined to communicate the sate of the software to its user. The components of a software (application and database) are transformed likewise, thus the state is defined for them too.
\begin{align*}
 	\mathbf{state} = Consistent\; s \: | \: Inconsistent \; s,  \\	s \lhd Software \vee s \lh Application \vee s \lhd Database
\end{align*}
Before the definition of the software consistency is provided, the notation of function transcription has to be introduced. Usually the definition of a function consists of two parts - an effect of the function and conditions when the effect occurs We decide to use following transcription, to simplify the notation and to improve understanding of functions:
\begin{align*}
f(x) =   \inference{conditions}{effect}
\end{align*}
The function querying the state (it means consistency) of a software is defined as:
\begin{align*}
 	\mathbf{consistent} : State \rightarrow Boolean \\
 	consistent(s) = \begin{cases}
 		\inference{s = Consistent(s)}{true}\\\\
 		\inference{s = Inconsistent(s)}{false}\\
 \end{cases}\\
 s \lhd State
\end{align*}
The consistency of application and database is discussed later in this paper. The definition of software state only is provided:
\begin{align*}
	\mathbf{state} : Software \rightarrow State \\
	state(s) = \begin{cases}
 		\inference{consistent(application(s)) \wedge \\ consistent(database(s)) \\ \wedge \rho(application(s)) = database(s)}{Consistent \; s}\\ \\
 		\inference{otherwise}{Inconsistent \; s}
 	\end{cases} \\ \\
\end{align*}

@@

\paragraph{Stored Data} A database consists not only from schema but also from data which are represented as rows in a table. A table row in our model is a tuple consisting of value pairs, which represents concrete value of concrete column. Each row contains a name of a table it belongs to.
\begin{align*}
	\mathbf{Row} = < refTable, pkValue, pair* > \\
	\mathbf{row} : Label \times Pairs \rightarrow Row \\ \\
	\mathbf{refTable} : Row \rightarrow Label \\
	refTable(row(l, n, ps) = l \\ \\
	\mathbf{pairs} : Row \rightarrow Pair* \\
	pairs(row(l, n, ps)) = ps \\ \\
	\mathbf{pkValue} : Row \rightarrow N \\
	pkValue(row(l, n, ps)) = n \\ \\
	 l \in Label, ps = Pair*, n \in N
\end{align*}
The value stored in concrete column of the row is represented by a pair, where the $refCol$ is a name of the column, a foreign key or its primary key and $value$ represents concrete value .
\begin{align*}
	\mathbf{Pair} = < refCol, value > \\
	[Label \times Value] \rightarrow Pair\\ \\
	\mathbf{reference} : Pair \rightarrow Label \\
	reference([l,val]) = l \\ \\
	\mathbf{value} : Pair \rightarrow Value \\ 
	value([l,val]) = val \\ \\
	l \in Label, val \in Value
\end{align*}
The definition of data allows definition of function $contains$ which verify if the table contains data in context of concrete database and $instantiated$, which search for instances of a class with given name and returns true if there are rows for the table in the database.
\begin{align*}
	\mathbf{contains} : Table \times Database \rightarrow Boolean \\
	contains(t, d) = \begin{cases}
			\inference{\exists r \in data(d) : refTable(r) = name(t) }{true} \\ \\
		 	false
 		\end{cases} \\ \\
 l \in Label, ps = Pair*, t \in tables(d), d \lhd Database
\end{align*}
\begin{align*}
	\mathbf{tableData} : Label \times Row* \rightarrow Row* \\
	tableData(l, r) = \begin{cases}
 		\inference{r = \varnothing}{\varnothing} \\
 		\inference{|r| > 1}{tableData(head(r)) \cup tableData(tail(r))}\\ \\
 		\inference{|r| = 1 \wedge refTable(r) = l}{r}\\\\
 		\inference{|r| = 1 \wedge refTable(r) \neq l}{\varnothing}
 \end{cases} \\ \\
	r \lhd Row*, l \in Label
\end{align*}
\begin{align*}
	\mathbf{instantiated} : Class \times Software \rightarrow Boolean \\
	instantiated(c, s) = \begin{cases} \inference{\exists t \in tables(database(s)) : name(t) = name(c) \\ \wedge contains(t, database(s))}{true} \\ \\
  false
 \end{cases} \\ \\
	 c \in classes(application(s)), s \lhd Software 
\end{align*}

@@

\subsection{Software Creation}
There are defined three transformations which are able to create a software: $addProperty$, $addAssociation$,  $newClass$. These three transformations can be used to create a software from a scratch. The last of them has no impact on stored data, whereas the rest of them can in some cases.
\paragraph{Add Property} Adding a property to database can change not only structure but stored data too, because a mandatory property can be added into a class with already existing instances, then a default value has to be added to all existing instances.
\begin{align*}
	\mathbf{addProperty} : Label \times Property \times State \rightarrow State \\
	\Psi(s, addProperty(l, p)) = application(s) \circ addProp(l,p) \\
	\Phi(s, addProperty(l, p)) = \begin{cases}
    		\inference{cardinality(p) \leq 1}{database(s) \bullet addColumn(l, \rho(p,d), d)} \\ \\
	    \inference{ \exists t \in tables(d) : name(t) = name(owningClass(p)) \\ \wedge mandatory(p) \wedge instantiated(owningClass(p)) \\ \wedge cardinality(p) \leq 1}{\begin{gathered}
   database(s) \bullet addTable(\rho(p,d), d) \\ \bullet \forall r \in row(owningClass(p)) :\\ insertRow(row(name(p), ["value", defaultValue(p)], \\ [name(p), value(primaryKey(r))])) 
    \end{gathered} } 
   \end{cases}\\
	s \lhd Software, l \in Label, p \in Properties
\end{align*}

\begin{align*}
\mathbf{addAsociation} : Label \times Association \times (Row \times Row) \times State \rightarrow State \\
\Psi(s, addAsociation(l, a, f_m)) = application(s) \circ addAssoc(l, a) \\
\Phi(s, addAsociation(l, a, f_m)) = database(s) \bullet insertAssoc(l, a, f_m)
\end{align*}

@@

\paragraph{Add Class} The $insertClass$ operation changes the structure of the database schema only, because the $insertAssoc$ transformation needs a mapping function to work properly, which is not part of the $newClass$ definition. The situation reflect the modeling praxis when the structure of a class is defined and then it is associations are created.
\begin{align*}
\mathbf{newClass} : Class \times State \rightarrow State \\
\Psi(s, newClass(c)) = application(s) \circ addClass(c) \\
\Phi(s, newClass(c)) = database(s)  \bullet addTable(\rho(c,d), d) \\ \bullet addColumn(name(c), \{\forall r \in singleProperties(c) | \rho(r,d)\}, d) \\ \bullet addTable(name(c), \{\forall r \in collections(c) | \rho(r,d)\}, d)  
\end{align*}

@@

\subsection{Software Decomposition}
\begin{align*}
	\mathbf{RemoveClass}: Label \times Software \rightarrow State  \\
	\Psi RemoveClass(l, s) = applications(s) \circ remClass(l) \\
	\Phi RemoveClass(l, s) = database(s) \bullet dropTable(l) \\
	l \in Label, s \in Software 
\end{align*}

\begin{align*}
	\mathbf{RemoveProperty} : Label \times Label \times State \rightarrow State \\
	\Psi RemoveProperty(l, l_p, s) =  applications(s) \circ  remProp(l, l_p) \\
	\Phi RemoveProperty(l, l_p, s) = \begin{cases}
		 \inference{cardinality(propertyByName(l_p, application(s)) \leq 1}{database(s) \bullet dropColumn(l, l_p)}  \\\\
		 \inference{cardinality(propertyByName(l_p, application(s)) >1}{database(s) \bullet dropTable(l)}
 	\end{cases}\\
 	l, l_p \in Label, s \lhd Software
\end{align*}

\begin{align*}
    \mathbf{RemoveAssociation} : Label \times Labels \times State \rightarrow State \\ 
    \Psi RemoveAssociation(l, l_a, s) = application(s) \circ remAss(l, l_a) \\
    \Phi RemoveAssociation(l, l_a, s) = \begin{cases}
     	\inference{a = associationByName(l, l_a, application(s)) \\ \wedge startCardinality(a) \leq 1 \\}{database(s) \bullet dropForeignKey(l_a, reference(a))} \\\\
     	\inference{a = associationByName(l, l_a, application(s)) \\ \wedge startCardinality(a) > 1}{database(s) \bullet dropTable(l_a)} 
     \end{cases}\\
    l_c, l_a \in Labels, s \lhd Software
\end{align*}

\subsection{Software Alternation}
\paragraph{Rename Class}
\begin{align*}
\mathbf{RenameClass} : Label \times Label \times State \rightarrow State \\ 
\Psi(RenameClass(l_o, l_n), s) = application(s) \circ renClass(l_o, l_n) \\
\Phi(RenameClass(l_o, l_n), s) = database(s) \bullet alterTable(l_o, l_n) \\ \\
\end{align*}

\paragraph{Rename Property}
\begin{align*}
	\mathbf{RenameProperty} : Label \times Label \times Label \times State \rightarrow State \\ \\
\Psi(RenameProperty(l_c, l_o, l_n, s)) = application(s) \circ renProp(l_c, l_o, l_n) \\
\Phi(RenameProperty(l_c, l_o, l_n, s)) = \begin{cases}
 	\inference{cardinality(propertyByName(l_c, l_o, application(s))) \leq 1}{database(s) \bullet alterColumn(l_c, l_o, l_n))} \\\\
 	\inference{cardinality(propertyByName(l_c, l_o, application(s))) > 1}{database(s) \bullet alterTable(l_o, l_n, database(s))}
 \end{cases}\\
l_c, l_o, l_n \in Label,  s \lhd Software
\end{align*}

\paragraph{Rename Association}
\begin{align*}
\mathbf{RenameAssociation} : Label \times Label \times Label \times State \rightarrow State \\
\Psi(RenameAssocaiation(l_c, l_o, l_n), s) = application(s) \circ renAssoc(l_c, l_o, l_n)\\
\Phi(RenameAssocaiation(l_c, l_o, l_n), s) = \begin{cases}
	\inference{\exists a  \in associationByName(application(s)) : \\
  name(a) = l_c \\ \wedge startCardinality(a) > 1 }{database(s) \bullet alterTable(l_c, l_o, l_n)}
 \\ \\
  \inference{\exists a  \in associationByName(application(s)) : \\
  name(a) = l_c \\ \wedge startCardinality(a) \leq 1 }{\begin{gathered}
database(s) \\ \bullet alterForeignKey(endClass(a) ,l_c, l_o, l_n)
\end{gathered}}
 \end{cases}
\\\\
%	alterAssoc(l_c, l_o, l_n, d) = \begin{cases}
%?? \inference{\exists t \in tables(a) : name(t) = l_c \\ \wedge \exists f \in fks(t) : name(c) = l_o \\ \wedge \forall e \in fks(t) : name(e) \neq l_n}{\begin{gathered}
%f.name = l_n 
%\end{gathered}}
%\\ \\
%\inference{\exists t \in tables(a) : name(t) = l_o \\ \wedge \forall e \in tables(t) : name(e) \neq l_n}{\begin{gathered}
%t.name = l_n 
%\end{gathered}}
% \end{cases}
% \\
l_c, l_o, l_n \in Label, a \lhd Applications, s \in Sates, d \lhd Database
\end{align*}

@@

The $CopyProperty$ function can be implemented as a transformation composed by operations for adding and removing property, nevertheless this composition would not work with instances, therefore transformation to update data are used.
\begin{align*}
	\mathbf{CopyProperty} : Label \times Label \times Label \times (Row \times Row) \times State \rightarrow State \\
	\Psi(CopyProperty(l_s, l_t, l_p, f_m), s) = \inference{\exists c \in classes(s) : name(c) = l_s \\ \wedge \exists p \in properties(c) : name(p) = l_p }{application(s) \circ addProp(l_t, p)} \\\\
	\Phi(CopyProperty(l_s, l_t, l_p, f_m), s) = \begin{cases}
		\inference{\exists p \in properties(c), c \in classes(s) : \\ name(p) = l_p \wedge cardinality(p) \leq 1 }{\begin{gathered}
			database(s) \bullet copyColumn(l_s, l_t, l_p) \\ \bullet copyValues(l_s, l_t, l_p, f_m) 
			\end{gathered}} \\ \\
		\inference{\exists p \in properties(c), c \in classes(s) : \\ name(p) = l_p \wedge cardinality(p) > 1}{\begin{gathered}
			database(s) \bullet copyTable(l_s, l_t, l_p) \\ \bullet copyRows(l_s, l_t, l_p, f_m) 
			\end{gathered}}
 \end{cases}
\end{align*}

>>>>

The software has to be in consistent state so its users could have benefit from its usage. The state of the software is defined to communicate the sate of the software to its user. The components of a software (application and database) are transformed likewise, thus the state is defined for them too.
\begin{align*}
 	\mathbf{state} = Consistent\; s \: | \: Inconsistent \; s,  \\	s \lhd Software \vee s \lh Application \vee s \lhd Database
\end{align*}
Before the definition of the software consistency is provided, the notation of function transcription has to be introduced. Usually the definition of a function consists of two parts - an effect of the function and conditions when the effect occurs We decide to use following transcription, to simplify the notation and to improve understanding of functions:
\begin{align*}
f(x) =   \inference{conditions}{effect}
\end{align*}
The function querying the state (it means consistency) of a software is defined as:
\begin{align*}
 	\mathbf{consistent} : State \rightarrow Boolean \\
 	consistent(s) = \begin{cases}
 		\inference{s = Consistent(s)}{true}\\\\
 		\inference{s = Inconsistent(s)}{false}\\
 \end{cases}\\
 s \lhd State
\end{align*}
The consistency of application and database is discussed later in this paper. The definition of software state only is provided:
\begin{align*}
	\mathbf{state} : Software \rightarrow State \\
	state(s) = \begin{cases}
 		\inference{consistent(app(s)) \wedge \\ consistent(db(s)) \\ \wedge \rho(app(s)) = db(s)}{Consistent \; s}\\ \\
 		\inference{otherwise}{Inconsistent \; s}
 	\end{cases} \\ \\
\end{align*}

@@

\paragraph{Stored Data} A database consists not only from schema but also from data which are represented as rows in a table. A table row in our model is a tuple consisting of value pairs, which represents concrete value of concrete column. Each row contains a name of a table it belongs to.
\begin{align*}
	\mathbf{Row} = < refTable, pkValue, pair* > \\
	\mathbf{row} : Label \times Pairs \rightarrow Row \\ \\
	\mathbf{refTable} : Row \rightarrow Label \\
	refTable(row(l, n, ps) = l \\ \\
	\mathbf{pairs} : Row \rightarrow Pair* \\
	pairs(row(l, n, ps)) = ps \\ \\
	\mathbf{pkValue} : Row \rightarrow N \\
	pkValue(row(l, n, ps)) = n \\ \\
	 l \in Label, ps = Pair*, n \in N
\end{align*}
The value stored in concrete column of the row is represented by a pair, where the $refCol$ is a name of the column, a foreign key or its primary key and $value$ represents concrete value .
\begin{align*}
	\mathbf{Pair} = < refCol, value > \\
	[Label \times Value] \rightarrow Pair\\ \\
	\mathbf{reference} : Pair \rightarrow Label \\
	reference([l,val]) = l \\ \\
	\mathbf{value} : Pair \rightarrow Value \\ 
	value([l,val]) = val \\ \\
	l \in Label, val \in Value
\end{align*}
The definition of data allows definition of function $contains$ which verify if the table contains data in context of concrete database and $instantiated$, which search for instances of a class with given name and returns true if there are rows for the table in the database.
\begin{align*}
	\mathbf{contains} : Table \times Database \rightarrow Boolean \\
	contains(t, d) = \begin{cases}
			\inference{\exists r \in data(d) : refTable(r) = name(t) }{true} \\ \\
		 	false
 		\end{cases} \\ \\
 l \in Label, ps = Pair*, t \in tables(d), d \lhd Database
\end{align*}
\begin{align*}
	\mathbf{tableData} : Label \times Row* \rightarrow Row* \\
	tableData(l, r) = \begin{cases}
 		\inference{r = \varnothing}{\varnothing} \\
 		\inference{|r| > 1}{tableData(head(r)) \cup tableData(tail(r))}\\ \\
 		\inference{|r| = 1 \wedge refTable(r) = l}{r}\\\\
 		\inference{|r| = 1 \wedge refTable(r) \neq l}{\varnothing}
 \end{cases} \\ \\
	r \lhd Row*, l \in Label
\end{align*}
\begin{align*}
	\mathbf{instantiated} : Class \times Software \rightarrow Boolean \\
	instantiated(c, s) = \begin{cases} \inference{\exists t \in tables(db(s)) : name(t) = name(c) \\ \wedge contains(t, db(s))}{true} \\ \\
  false
 \end{cases} \\ \\
	 c \in classes(app(s)), s \lhd Software 
\end{align*}

@@

\subsection{Software Creation}
There are defined three transformations which are able to create a software: $addProperty$, $addAssociation$,  $newClass$. These three transformations can be used to create a software from a scratch. The last of them has no impact on stored data, whereas the rest of them can in some cases.
\paragraph{Add Property} Adding a property to database can change not only structure but stored data too, because a mandatory property can be added into a class with already existing instances, then a default value has to be added to all existing instances.
\begin{align*}
	\mathbf{addProperty} : Label \times Property \times State \rightarrow State \\
	\Psi(s, addProperty(l, p)) = app(s) \circ addProp(l,p) \\
	\Phi(s, addProperty(l, p)) = \begin{cases}
    		\inference{cardinality(p) \leq 1}{db(s) \bullet addColumn(l, \rho(p,d), d)} \\ \\
	    \inference{ \exists t \in tables(d) : name(t) = name(owningClass(p)) \\ \wedge mandatory(p) \wedge instantiated(owningClass(p)) \\ \wedge cardinality(p) \leq 1}{\begin{gathered}
   db(s) \bullet addTable(\rho(p,d), d) \\ \bullet \forall r \in row(owningClass(p)) :\\ insertRow(row(name(p), ["value", defaultValue(p)], \\ [name(p), value(primaryKey(r))])) 
    \end{gathered} } 
   \end{cases}\\
	s \lhd Software, l \in Label, p \in Properties
\end{align*}

\begin{align*}
\mathbf{addAsociation} : Label \times Association \times (Row \times Row) \times State \rightarrow State \\
\Psi(s, addAsociation(l, a, f_m)) = app(s) \circ addAssoc(l, a) \\
\Phi(s, addAsociation(l, a, f_m)) = db(s) \bullet insertAssoc(l, a, f_m)
\end{align*}

@@

\paragraph{Add Class} The $insertClass$ operation changes the structure of the database schema only, because the $insertAssoc$ transformation needs a mapping function to work properly, which is not part of the $newClass$ definition. The situation reflect the modeling praxis when the structure of a class is defined and then it is associations are created.
\begin{align*}
\mathbf{newClass} : Class \times State \rightarrow State \\
\Psi(s, newClass(c)) = app(s) \circ addClass(c) \\
\Phi(s, newClass(c)) = db(s)  \bullet addTable(\rho(c,d), d) \\ \bullet addColumn(name(c), \{\forall r \in singleProperties(c) | \rho(r,d)\}, d) \\ \bullet addTable(name(c), \{\forall r \in collections(c) | \rho(r,d)\}, d)  
\end{align*}

@@

\subsection{Software Decomposition}
\begin{align*}
	\mathbf{RemoveClass}: Label \times Software \rightarrow State  \\
	\Psi RemoveClass(l, s) = applications(s) \circ remClass(l) \\
	\Phi RemoveClass(l, s) = db(s) \bullet dropTable(l) \\
	l \in Label, s \in Software 
\end{align*}

\begin{align*}
	\mathbf{RemoveProperty} : Label \times Label \times State \rightarrow State \\
	\Psi RemoveProperty(l, l_p, s) =  applications(s) \circ  remProp(l, l_p) \\
	\Phi RemoveProperty(l, l_p, s) = \begin{cases}
		 \inference{cardinality(propertyByName(l_p, app(s)) \leq 1}{db(s) \bullet dropColumn(l, l_p)}  \\\\
		 \inference{cardinality(propertyByName(l_p, app(s)) >1}{db(s) \bullet dropTable(l)}
 	\end{cases}\\
 	l, l_p \in Label, s \lhd Software
\end{align*}

\begin{align*}
    \mathbf{RemoveAssociation} : Label \times Labels \times State \rightarrow State \\ 
    \Psi RemoveAssociation(l, l_a, s) = app(s) \circ remAss(l, l_a) \\
    \Phi RemoveAssociation(l, l_a, s) = \begin{cases}
     	\inference{a = associationByName(l, l_a, app(s)) \\ \wedge startCardinality(a) \leq 1 \\}{db(s) \bullet dropForeignKey(l_a, reference(a))} \\\\
     	\inference{a = associationByName(l, l_a, app(s)) \\ \wedge startCardinality(a) > 1}{db(s) \bullet dropTable(l_a)} 
     \end{cases}\\
    l_c, l_a \in Labels, s \lhd Software
\end{align*}

\subsection{Software Alternation}
\paragraph{Rename Class}
\begin{align*}
\mathbf{RenameClass} : Label \times Label \times State \rightarrow State \\ 
\Psi(RenameClass(l_o, l_n), s) = app(s) \circ renClass(l_o, l_n) \\
\Phi(RenameClass(l_o, l_n), s) = db(s) \bullet alterTable(l_o, l_n) \\ \\
\end{align*}

\paragraph{Rename Property}
\begin{align*}
	\mathbf{RenameProperty} : Label \times Label \times Label \times State \rightarrow State \\ \\
\Psi(RenameProperty(l_c, l_o, l_n, s)) = app(s) \circ renProp(l_c, l_o, l_n) \\
\Phi(RenameProperty(l_c, l_o, l_n, s)) = \begin{cases}
 	\inference{cardinality(propertyByName(l_c, l_o, app(s))) \leq 1}{db(s) \bullet alterColumn(l_c, l_o, l_n))} \\\\
 	\inference{cardinality(propertyByName(l_c, l_o, app(s))) > 1}{db(s) \bullet alterTable(l_o, l_n, db(s))}
 \end{cases}\\
l_c, l_o, l_n \in Label,  s \lhd Software
\end{align*}

\paragraph{Rename Association}
\begin{align*}
\mathbf{RenameAssociation} : Label \times Label \times Label \times State \rightarrow State \\
\Psi(RenameAssocaiation(l_c, l_o, l_n), s) = app(s) \circ renAssoc(l_c, l_o, l_n)\\
\Phi(RenameAssocaiation(l_c, l_o, l_n), s) = \begin{cases}
	\inference{\exists a  \in associationByName(app(s)) : \\
  name(a) = l_c \\ \wedge startCardinality(a) > 1 }{db(s) \bullet alterTable(l_c, l_o, l_n)}
 \\ \\
  \inference{\exists a  \in associationByName(app(s)) : \\
  name(a) = l_c \\ \wedge startCardinality(a) \leq 1 }{\begin{gathered}
db(s) \\ \bullet alterForeignKey(endClass(a) ,l_c, l_o, l_n)
\end{gathered}}
 \end{cases}
\\\\
%	alterAssoc(l_c, l_o, l_n, d) = \begin{cases}
%?? \inference{\exists t \in tables(a) : name(t) = l_c \\ \wedge \exists f \in fks(t) : name(c) = l_o \\ \wedge \forall e \in fks(t) : name(e) \neq l_n}{\begin{gathered}
%f.name = l_n 
%\end{gathered}}
%\\ \\
%\inference{\exists t \in tables(a) : name(t) = l_o \\ \wedge \forall e \in tables(t) : name(e) \neq l_n}{\begin{gathered}
%t.name = l_n 
%\end{gathered}}
% \end{cases}
% \\
l_c, l_o, l_n \in Label, a \lhd Applications, s \in Sates, d \lhd Database
\end{align*}

@@

The $CopyProperty$ function can be implemented as a transformation composed by operations for adding and removing property, nevertheless this composition would not work with instances, therefore transformation to update data are used.
\begin{align*}
	\mathbf{CopyProperty} : Label \times Label \times Label \times (Row \times Row) \times State \rightarrow State \\
	\Psi(CopyProperty(l_s, l_t, l_p, f_m), s) = \inference{\exists c \in classes(s) : name(c) = l_s \\ \wedge \exists p \in properties(c) : name(p) = l_p }{app(s) \circ addProp(l_t, p)} \\\\
	\Phi(CopyProperty(l_s, l_t, l_p, f_m), s) = \begin{cases}
		\inference{\exists p \in properties(c), c \in classes(s) : \\ name(p) = l_p \wedge cardinality(p) \leq 1 }{\begin{gathered}
			db(s) \bullet copyColumn(l_s, l_t, l_p) \\ \bullet copyValues(l_s, l_t, l_p, f_m) 
			\end{gathered}} \\ \\
		\inference{\exists p \in properties(c), c \in classes(s) : \\ name(p) = l_p \wedge cardinality(p) > 1}{\begin{gathered}
			db(s) \bullet copyTable(l_s, l_t, l_p) \\ \bullet copyRows(l_s, l_t, l_p, f_m) 
			\end{gathered}}
 \end{cases}
\end{align*}
